% File: itProjectProposal.tex
\chapter{Project Proposal}
\label{ch:proposal}

\section{Project Title}
\textbf{Title:} Cloudflow

\section{Project Description}
The goal of this project is to develop a lightweight, functional portfolio creator that not only displays the day’s top-performing stocks but also allows users to build and manage a customized investment portfolio containing a mix of short- and long-term investments. A critical component of this application is secure user management, including account creation and authentication. To
ensure security is embedded into the development lifecycle, we will integrate DevSecOps practices such as automated vulnerability scanning (e.g., SonarQube or Snyk) during CI/CD pipelines, container image scanning (e.g., Trivy), and secrets management (e.g., HashiCorp Vault). These tools will help us detect risks early, enforce secure coding standards, and protect sensitive financial and user data.

\section{Sample Tasks and Tools}
\begin{itemize}
    \item \textbf{Source Control:} GitHub
    \item \textbf{Testing:} Jest for JavaScript unit tests
    \item \textbf{Deployment:} Docker + AWS App Runner
    \item \textbf{Database:} PostgreSQL
    \item \textbf{Monitoring:} AWS CloudWatch
\end{itemize}

\section{Evaluation Criteria}
The project will be evaluated based on:
\begin{enumerate}
    \item Building a working application (40 pts).
    \item Using DevOps tools and comparisons (20 pts).
    \item Environment setup (AWS/containers) (20 pts).
    \item Operational dashboard (20 pts).
    \item SWOT chart analysis (20 pts).
\end{enumerate}